---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bioinform

<!-- badges: start -->
<!-- badges: end -->

The goal of bioinform, short for "Bioinformatics," is to provide functions that can be applied to biological and ecological datasets. 

## Installation

For basic installation, use the following code:

```{r}
# install.packages("devtools")
devtools::install_github("nb97/bioinform")
```

## Example and usage

This is a basic example which shows you how to apply Bioinform when running qPCR. The Cq average obtained is how many cycles that a sample takes to amplify. The Cq average can be used to find the DNA concentration. 

```{r example}
library(devtools)
library(bioinform)

Cq_value <- function(x){
  Cq_avg <- ((x) -22.245)/(-3.45)
  return(Cq_avg)
}

Cq_value(30)

```

# For inputting data
This is best applied to values pulled from excel or csv fiies. Therefore, it could also be helpful to import data using:
```{r cars}
#read.csv()
#readxl::read_xls()
```
NOTE: The purrr package is imported with this dataset to give ability to read lists in addition to numeric vectors. 

# Vignette 
You can access more information about bioinform package through the vignette. Use this command for istallation:
```{r}
#install.packages("devtools")
#devtools::install_github("nb97/bioinform", build_vignettes = TRUE)
```

And to read the vignette:
```{r}
library(bioinform)
browseVignettes("bioinform")
```


# Citation 
```{r}
citation("bioinform")
```
## Code of Conduct
A code of conduct is included. It is a pledge that conributors agree upon. Guidelines are layed out within the document. 
