---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bioinform

<!-- badges: start -->
<!-- badges: end -->

The goal of bioinform, short for "Bioinformatics," is to provide functions that can be applied to biological and ecological datasets. 

## Installation

For basic installation, use the following code:

```{r}
# install.packages("devtools")
devtools::install_github("nb97/bioinform")
```

## Example and usage

This is a basic example which shows you how to apply Bioinform when running qPCR. The Cq average obtained is how many cycles that a sample takes to amplify. The Cq average can be used to find the DNA concentration. 

```{r example}
library(devtools)
library(bioinform)

Cq_value <- function(x){
  Cq_avg <- ((x) -22.245)/(-3.45)
  return(Cq_avg)
}

Cq_value(30)

```
# Tests
This test shows that the expected value (6.221) by manually solving for Cq with x=5 would equal the same as usign Cq_value function.

# Equation 
To find the Cq one must solve for x in the following equation: 
x = (Cq - 22.245) / -3.4564	

-22.245 and -3.45 are derived from the average Cq on a standard curve. These standards are at a serial dilution starting at 10ng/uL and decreasing 10x with each standard. The second standard is diluted to 1ng/uL, the third to 0.1ng/uL, forth to 0.01ng/Ul, etc.

These standards were developed by targeting the CO1 gene is Chinook Salmon (Oncorhynchus tshawytscha). 

This equaiton is applicable to Natalie Benoit's M.Sc. however it can be maniupated and applied to similar studies with slight modification to the equation. 

# For inputting data
This is best applied to values pulled from excel or csv fiies. Therefore, it could also be helpful to import data using:
```{r cars}
#read.csv()
#readxl::read_xls()
```
NOTE: The purrr package is imported with this dataset to give ability to read lists in addition to numeric vectors. 

# Vignette 
You can access more information about bioinform package through the vignette. Use this command for istallation:
```{r}
#install.packages("devtools")
#devtools::install_github("nb97/bioinform", build_vignettes = TRUE)
```

And to read the vignette:
```{r}
library(bioinform)
browseVignettes("bioinform")
```


# Citation 
```{r}
citation("bioinform")
```
## Code of Conduct
A code of conduct is included. It is a pledge that conributors agree upon. Guidelines are layed out within the document. 
